Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
wording

Started in 2009, \textit{scikit-learn} counts a large team of volunteer
international developers mainly consisting of scientists and researchers from
various fields (e.g., machine learning, natural language processing or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code and/or documentation fixes or improvements.
Because of this large base of developers, important efforts are deployed to make
the project maintainable. In particular, we emphasize on high-quality and well-documented
code  in order to ease future developments by external contributors.
\textcolor{red}{TODO: Mention some good coding practices (automatic testing, code
reviews, etc)}

>>>>

Started in 2009, \textit{scikit-learn} is developed by a large and
international team of volunteers, mostly researchers from
various fields (e.g., machine learning, natural language processing, or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency, unit-test coverage. In
addition, complete documentation and examples are required for all
features. Finally, any addition to the code base goes through thorough
code review.
